Feeding Dynamic Behavior into Optimization: Simulation-based Multi-objective Overtime Planning

### 2014-09-04 data/result/Article/Latex/Article.tex
.

The {\^A12} standardized effect-size was calculated for pair-wise comparisons between NSGAII and each OMS for all quality indicators. Results are presented in Table III, denoting the chances of NSGAII to produce higher I$_C$ and I$_{HV}$ and lower I$_{GD}$ than the related OMS. {\^A}12 is very high and favors NSGAII for all instances for I$_{HV}$ and I$_{GD}$. It also strongly favors NSGAII in terms of $I_C$ if compared to MAR and CPM, except on PARM (a draw on effect-size among both OMS and NSGAII). However, {\^A}12 tells a different story for I$_{C}$ between NSGAII and SH, clearly favoring SH for the largest instance. Effect-sizes are in agreement with former results indicating that MAR and CPM are not effective OMS. They also provide additional evidence on the differences between NSGAII and SH: if there is enough time to run the optimization process, NSGAII can produce Pareto fronts which present more diversity and are closer to optimal than those resulting from SH, but the latter can quickly provide an approximation for the reference front. Thus, the industry has good reasons for concentrating overtime on the second half of project schedules, but it can improve its practices by combining SH with our approach in order to provide more overtime allocation alternatives for the decision maker.

>>>>

The {\^A12} standardized effect-size was calculated for pair-wise comparisons between NSGAII and each OMS for all quality indicators. Results are presented in Table III, denoting the chances of NSGAII to produce higher I$_C$ and I$_{HV}$ and lower I$_{GD}$ than the related OMS. {\^A}12 is very high and favors NSGAII for all instances for I$_{HV}$ and I$_{GD}$. It also strongly favors NSGAII in terms of $I_C$ if compared to MAR and CPM, except on PARM (a draw on effect-size among both OMS and NSGAII). However, {\^A}12 tells a different story for I$_{C}$ between NSGAII and SH, clearly favoring SH for the largest instance. Effect-sizes are in agreement with former results indicating that MAR and CPM are not effective OMS. They also provide additional evidence on the effectiveness of NSGAII and SH: if there is enough time to run the optimization, NSGAII can produce Pareto fronts which are richer in diversity and closer to optimal than those resulting from SH, but the latter can quickly provide an approximation for the reference front. Thus, the industry has good reasons for concentrating overtime on the second half of project schedules, though it can improve its practices by combining SH with our approach in order to provide more overtime allocation alternatives for the decision maker.
